Algorithmic and Economic Aspects of the Internet

### 2012-12-03 report/paper.tex
Made more words.

-- insert explanation about that here.

>>>>

\subsection{AA v Shaver} One very noticable trend in our analysis is when AA
is pitched against the Shaver algorithm. In all of our experiments where trades
occurred, Shaver made more profit than AA. In this section, we explore the
reasons why Shaver so completely outclasses our implemetation of AA.

Shaver is designed to make "close shave" bids and asks by slightly out-bidding
the best bid on the market. This is similar to how AA's aggressiveness is
supposed to operate; when a bid is placed that out-bids the bot, the price is
adjusted so that the bot out-bids the previous bid in the following round
(unless such a bid would exceed the bot's limit price). This aggressiveness
behaviour increases the chance of a trade and thus increases profit.

We show 3 cases here:
\begin{enumerate}
\item 1 AA bot v. 1 Shaver bot
\item 1 AA bot v. 10 Shaver bots
\item 10 AA bots v. 10 Shaver bots
\end{enumerate}

\subsubsection{1 v 1} No trading occurs in this experiment. In the graphs
below, you can see the shouts made by the bots. The Shaver buyer and seller
traders tend toward the equilibrium price over time but don't manage to reach
it before the market session ends. The AA bot makes very few trades and is
always out-bid / out-asked by Shaver.

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_bids.png}
\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the bids made.}
\end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_asks.png}
\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the asks made.}
\end{figure}

\subsubsection{1 v Many} In these experiments, trading starts at around round
90. In the graphs below, we see that the Shaver bots tend towards the
equilibrium much faster than when there was only one bot; this is likely due to
there being 10 Shaver bots which are all trying to out-bid each other. When the
bids and asks converge, the Shaver bots invariably trade with themselves. Our
AA implementation is excluded from trading as it can't adjust its
aggressiveness quickly enough. Not all Shaver bots are engaged in making actual
trades at all times, the horizontal lines of bids / asks on the graphs indicate
that a Shaver bot is placing shouts at its limit price.

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_bids.png}
\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the bids made.}
\end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_asks.png}
\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the asks made.}
\end{figure}

Our AA implmentation again demonstrates how it is not tending to the
equilibrium logarithmically as it shold be. Were it functioning correctly, our
AA implementation should have placed bids that were higher (or asks that were
smaller) just after those Shaver placed. This is because AA is designed to
alter its aggressiveness such that it can make competitive shouts in subsequent
rounds, however, it fails to do this. In other words, Adaptive Aggressive is
failing to change it's aggressiveness adaptively.

\subsubsection{Many v Many} Again, trading begins at around round 90. We see
the same pattern as we do in the previous experiment except that AA is making
more bids / asks. On this occasion we see that AA actually manages to make a
few profitable trades between rounds 90 and 140 before being swamped by the
simpler and more effective aggressiveness function of the correctly implemented
Shaver bot. These few trades are more by chance than by design; the dip in bid
price would have intersected with the poorly adapting AA bot allowing AA to
place bids that would be accepted by the seller Shaver traders.
